Implementing XBF: An Efficient Self-Describing Binary Format

### 2023-08-09 docs/paper.tex
Update paper

@@

@@

\begin{table}[htbp]
	\begin{center}
		\begin{tabular}{|c|c|c|}
			\hline
			\textbf{Format} & \textbf{Avg Time (ms)} & \textbf{Bytes Read} \\
			\hline
			CSV             & 18.931802              & 16411               \\
			MessagePack     & 11.220957              & 15565               \\
			CBOR            & 16.957873              & 25507               \\
			JSON            & 21.912745              & 31180               \\
			XML             & 21.873043              & 43699               \\
			XBF             & 11.322245              & 14686               \\
			\hline
		\end{tabular}
	\end{center}\label{time_and_bytes}
\end{table}

\begin{table}[htbp]
	\begin{center}
		\begin{tabular}{|c|c|c|}
			\hline
			\textbf{Format} & \textbf{Overhead (bytes)} & \textbf{Percent Overhead} \\
			\hline
			CSV             & 1823                      & 11.1084                   \\
			MessagePack     & 977                       & 6.2769                    \\
			CBOR            & 10919                     & 42.8079                   \\
			JSON            & 16592                     & 53.2136                   \\
			XML             & 29111                     & 66.6171                   \\
			XBF             & 98                        & 0.6673                    \\
			\hline
		\end{tabular}
	\end{center}\label{overhead}
\end{table}

>>>>

Similar to CSV (cite here?), we send a single header up front, followed by all of the data. For a primitive type there isn't much savings here, but there are massive savings with vectors and structs. With a vector the metadata is a discriminant indicating a vector is being sent, which is then follwed by the metadata for its internal type. This process continues recursively if the inner type (or any of its inner types) contains a vector or struct, ensuring that all metadata necessary to represent the data coming afterwards is received up front. The data is then sent in a single continuous block, something after this...

@@

\subsection{Primitives}

The implementation of primitives is a tagged union of all possible primitive types, mapping the XBF type to the Rust native equivalent as shown in Table \ref{type_map}. The exceptions are the 256 bit integer types, which do not have an analog, and are instead represented by an array of four unsigned 64 bit integers.

Metadata for integers was an enumeration of the possible metadata discriminants, ranging from 0 to 16, represented as unsigned 8 bit integers.

\begin{table}[htbp]
	\caption{XBF Type Map}\label{type_map}
	\begin{center}
		\begin{tabular}{|c|c|}
			\hline
			\textbf{XBF Type} & \textbf{Rust Type}          \\
			\hline
			Boolean           & bool                        \\
			U8                & u8                          \\
			U16               & u16                         \\
			U32               & u32                         \\
			U64               & u64                         \\
			U128              & u128                        \\
			U256              & [u64; 4]                    \\
			I8                & i8                          \\
			I16               & i16                         \\
			I32               & i32                         \\
			I64               & i64                         \\
			I128              & i128                        \\
			I256              & [u64; 4]                    \\
			F32               & f32                         \\
			F64               & f64                         \\
			Bytes             & Vec\textless u8\textgreater \\
			String            & String                      \\
			\hline
		\end{tabular}
	\end{center}
\end{table}

\subsection{Vectors}

\subsection{Structs}

@@

\begin{table}[htbp]
	\caption{Average Time and Bytes Read}
	\begin{center}
		\begin{tabular}{|c|c|c|}
			\hline
			\textbf{Format} & \textbf{Avg Time (ms)} & \textbf{Bytes Read} \\
			\hline
			CSV             & 18.931802              & 16411               \\
			MessagePack     & 11.220957              & 15565               \\
			CBOR            & 16.957873              & 25507               \\
			JSON            & 21.912745              & 31180               \\
			XML             & 21.873043              & 43699               \\
			XBF             & 11.322245              & 14686               \\
			\hline
		\end{tabular}
	\end{center}\label{time_and_bytes}
\end{table}

\begin{table}[htbp]
	\caption{Format Overheads}
	\begin{center}
		\begin{tabular}{|c|c|c|}
			\hline
			\textbf{Format} & \textbf{Overhead (bytes)} & \textbf{Percent Overhead} \\
			\hline
			CSV             & 1823                      & 11.1084                   \\
			MessagePack     & 977                       & 6.2769                    \\
			CBOR            & 10919                     & 42.8079                   \\
			JSON            & 16592                     & 53.2136                   \\
			XML             & 29111                     & 66.6171                   \\
			XBF             & 98                        & 0.6673                    \\
			\hline
		\end{tabular}
	\end{center}\label{overhead}
\end{table}
